\chapter*{\centering Task 1}
\addcontentsline{toc}{chapter}{Task 1}
\begin{enumerate}
	\item{\textbf{Virus}} \\
	A type of malicious software program (malware) that, when executed, replicates itself by modifying other computer programs and inserting its own code. When this replication succeeds, the affected areas are then said to be "infected" with a computer virus. Viruses can cause various types of damage, such as corrupting or deleting data, spreading to other systems, and more.
	\item{\textbf {Worm }}\\
	A standalone malware computer program that replicates itself in order to spread into other computers. Unlike a computer virus, it does not need to attach itself to an existing program. Worms often use network connections to spread and can cause harm by consuming bandwidth, overloading systems, or delivering additional payloads, such as viruses or other malware.
	\item{\textbf {Trojan Horse}} \\
	A type of malware that is disguised as legitimate software. Users are typically tricked into loading and executing it on their systems. Once activated, Trojans can perform a variety of malicious actions, such as stealing data, damaging systems, or creating backdoors for other malware to enter.
	\item{\textbf {Spyware}} \\
	A type of malware that secretly observes the user's activities without permission and sends the collected information to a third party. Spyware can monitor and collect various types of data, such as keystrokes, screen captures, and login credentials, often leading to privacy breaches and identity theft.
\end{enumerate}