\chapter*{ \centering Task 4}
\addcontentsline{toc}{chapter}{Task 4}

\section*{VIRUS AND HOAX EMAIL SERVICES}
\subsection*{Message That a Threat is a Hoax}

Dear Team,\\

I hope this message finds you well. It has come to our attention that there is a circulating email warning about a new virus threat. After thorough investigation, we have determined that this email is a hoax. \\

Here are some tips to help you determine if future messages are real or fake:\vspace{.2cm}
\begin{enumerate}
	\item
	Verify the Source: Always check the sender's email address and ensure it matches the official domain of the supposed sender.
	\item
	Look for Red Flags: Be wary of urgent language, requests for personal information, or prompts to click on unfamiliar links.
	\item
	Check for Errors: Many hoax emails contain spelling and grammatical errors.
	\item
	Cross-Reference: Search online for keywords from the email along with the word "hoax" to see if others have reported it.
	\item
	Consult IT: If you are unsure about an email, do not hesitate to contact the IT department for verification.
\end{enumerate}
By staying vigilant and following these steps, we can protect ourselves from potential scams and misinformation. \\
\\
Best regards,\\
Erzoah Gaius Junior\\
Executive Manager\\
(0533876110)\\


\subsection*{Message That a Threat is a Real}
Dear Team, \\

I hope this message finds you well. My name is Erzoah Gaius Junior and I am your IT Specialist. We have recently been alerted to a serious virus threat that could potentially compromise our network security. This threat has been confirmed by [Source of Information], and it is crucial that we take immediate action to protect ourselves. \\
Warning
The virus in question is nicknamed “THE END” and it can spread through email attachments and malicious links. It has the capability to steal sensitive information and disrupt our systems.\\
Steps to Protect Yourself:\\
\begin{enumerate}
	\item
	Do Not Open Suspicious Emails: Be cautious of emails from unknown senders, especially those with attachments or links.
	\item
	 Update Your Software: Ensure your antivirus software is up to date. Our IT team has pushed the latest updates, but please verify that your systems are running the latest versions.
	 \item
	 Report Suspicious Activity: If you receive a suspicious email or notice unusual activity on your device, report it immediately to the IT department.
	 \item
	 Practice Safe Browsing: Avoid visiting untrusted websites and refrain from downloading software from unreliable sources.
\end{enumerate}
For more detailed information on this threat and how to safeguard your data, please refer to the following resources:\\
Email of IT Specialist:\url{jerzo204@gmail.com}\\
Contact: 0509894360
\\Your cooperation and vigilance are critical in keeping our organization secure. If you have any questions or need further assistance, please do not hesitate to reach out.
\\
Stay safe, \\
Erzoah Gaius Junior\\
IT Specialist\\
0509884360
